### 2020-02-17 README.Rmd
unfinished summary_dictionary

```{r example}
library(oolong)
library(stm)
newsgroup_stm
```

@@

```{r step0, eval = FALSE}
require(quanteda)
require(stm)
dfm(newsgroup5$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 5, max_docfreq = 1000) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> newsgroup5_dfm
docvars(newsgroup5_dfm, "title") <- newsgroup5$title
newsgroup5_dfm %>% convert(to = "stm", omit_empty = FALSE) -> newsgroup5_stm
newsgroup_stm <- stm(newsgroup5_stm$documents, newsgroup5_stm$vocab, data =newsgroup5_stm$meta, K = 10, seed = 42)
```

@@

```{r}
require(quanteda)
require(dplyr)
gold_standard <- oolong_test$turn_gold()
dfm(gold_standard, remove_punct = TRUE) %>% dfm_lookup(afinn) %>% quanteda::convert(to = "data.frame") %>%
    mutate(matching_word_valence = (neg5 * -5) + (neg4 * -4) + (neg3 * -3) + (neg2 * -2) + (neg1 * -1)
           + (zero * 0) + (pos1 * 1) + (pos2 * 2) + (pos3 * 3) + (pos4 * 4) + (pos5 * 5),
           base = ntoken(gold_standard, remove_punct = TRUE), afinn_score = matching_word_valence / base) %>%
    pull(afinn_score) -> all_afinn_score
all_afinn_score
```

@@

@@

```{r, include = FALSE}
oolong_test$.__enclos_env__$test_content$gold_standard$answer <- sample(1:5, 20, replace = TRUE)
```

```{r}
oolong_test$lock()
oolong_test$
```

>>>>

```{r echo = FALSE}
library(oolong)
library(stm)
library(quanteda)
library(dplyr)
```

```{r example}
newsgroup_stm
```

@@

```{r step0, eval = FALSE}
dfm(newsgroup5$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 5, max_docfreq = 1000) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> newsgroup5_dfm
docvars(newsgroup5_dfm, "title") <- newsgroup5$title
newsgroup5_dfm %>% convert(to = "stm", omit_empty = FALSE) -> newsgroup5_stm
newsgroup_stm <- stm(newsgroup5_stm$documents, newsgroup5_stm$vocab, data =newsgroup5_stm$meta, K = 10, seed = 42)
```

@@

```{r}
gold_standard <- oolong_test$turn_gold()
dfm(gold_standard, remove_punct = TRUE) %>% dfm_lookup(afinn) %>% quanteda::convert(to = "data.frame") %>%
    mutate(matching_word_valence = (neg5 * -5) + (neg4 * -4) + (neg3 * -3) + (neg2 * -2) + (neg1 * -1)
           + (zero * 0) + (pos1 * 1) + (pos2 * 2) + (pos3 * 3) + (pos4 * 4) + (pos5 * 5),
           base = ntoken(gold_standard, remove_punct = TRUE), afinn_score = matching_word_valence / base) %>%
    pull(afinn_score) -> all_afinn_score
all_afinn_score
```

@@

```{r, include = FALSE}
set.seed(46709394)
```

@@

```{r, include = FALSE}
oolong_test$.__enclos_env__$private$test_content$gold_standard$answer <- sample(1:5, 20, replace = TRUE)
```

```{r}
oolong_test$lock()
gold_standard <- oolong_test$turn_gold()
docvars(gold_standard, "target_value")
```

```{r}
summarize_gold_standard(gold_standard)
```
